A meta-analysis of mental rotation ability in the first years of life

### 2022-04-27 code/analysis.Rmd
Fix regression plot

```{r, fig_regression}
# Get draws from the posterior distribution
draws_reg <- epred_draws(
  res_brm_reg,
  dat_reg,
  ndraws = n_draws,
  re_formula = NA
)

@@

  # Regression lines and HPDIs - Habituation tasks
  stat_lineribbon(
    aes(y = .epred, color = gender_task),
    data = draws_reg,
    alpha = .4,
    point_interval = "mean_hdi"
  ) +
  # Individual study effect sizes - Habituation tasks
  geom_point(aes(color = gender_task, size = ni), shape = 0) +
  scale_color_manual(
    values = habituation_colors,
    breaks = names(habi_colors),
    labels = c("Females", "Males", "Mixed gender"),
    na.value = NA
  ) +
  guides(color = guide_legend(
    title = "Habituation tasks",
    override.aes = list(fill = NA),
    order = 1
  )) +

>>>>

```{r, fig_regression}
# Get draws from the posterior distribution
draws_reg <- epred_draws(
  res_brm_reg,
  dat_reg,
  ndraws = NULL,
  re_formula = NA
)

@@

  # Regression lines and HPDIs - Habituation tasks
  stat_lineribbon(
    aes(y = .epred, color = gender_task),
    data = draws_reg,
    alpha = .4,
    point_interval = "mean_hdi"
  ) +
  # Individual study effect sizes - Habituation tasks
  geom_point(aes(color = gender_task, size = ni), shape = 0) +
  scale_color_manual(
    values = habi_colors,
    breaks = names(habi_colors),
    labels = c("Females", "Males", "Mixed gender"),
    na.value = NA
  ) +
  guides(color = guide_legend(
    title = "Habituation tasks",
    override.aes = list(fill = NA),
    order = 1
  )) +
